My title

### 2024-11-24 paper/paper.qmd
model chage to OLR

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages("arrow")
#install.packages("tidyverse")
#install.packages("haven")
#install.packages("modelsummary")
#install.packages("kableExtra")
#install.packages("rstanarm")
#install.packages("bayesplot")
#install.packages("ggplot2")
#install.packages("brant")
#install.packages("pscl")

library(arrow)
library(tidyverse)
library(haven)
library(tidyverse)
library(palmerpenguins)
library(modelsummary)
library(kableExtra)
library(rstanarm)
library(bayesplot)
library(ggplot2)
library(brant)
library(pscl)

@@

```{r}

@@

Our results are summarized in

@@

>>>>

```{r}
#| include: false
#| warning: false
#| message: false

#install.packages("rstanarm")
#install.packages("modelsummary")
library(modelsummary)
library(rstanarm)

@@

@@

Our results are summarized in @tbl-modelresults

@@

bayesian_model <- readRDS(file = here::here ("models/bayesian_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Summary of the Ordinal Logistic regression model"
#| warning: false

# Install necessary packages if not already installed
#install.packages("broom.mixed")
#install.packages("kableExtra")

# Load the packages
library(broom.mixed)
library(kableExtra)

# Generate a tidy summary of your Bayesian model
tidy_summary <- tidy(
  bayesian_model, 
  conf.int = TRUE,      # Include credible intervals
  conf.level = 0.95     # Set confidence level to 95%
)

# Render the summary table as a nice HTML/LaTeX table
tidy_summary %>%
  kable(
    caption = "Bayesian Model Summary with Credible Intervals",
    digits = 2,             # Round numbers to 2 decimal places
    col.names = c("Parameter", "Estimate", "Std. Error", "Lower 95% CI", "Upper 95% CI")  # Rename columns
  ) %>%
  kable_styling(
    full_width = FALSE,
    bootstrap_options = c("striped", "hover", "condensed")
  )
